---
title: "cmr"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Programmatic access to [Common Metadata Repositories](https://wiki.earthdata.nasa.gov/display/CMR/Common+Metadata+Repository+Home) from R

## Requirements

+ [R v4.1+](https://www.r-project.org/)

+ [httr](https://CRAN.R-project.org/package=httr)
+ [base64enc](https://CRAN.R-project.org/package=base64enc)
+ [yaml](https://CRAN.R-project.org/package=yaml)
+ [rlang](https://CRAN.R-project.org/package=rlang)
+ [dplyr](https://CRAN.R-project.org/package=dplyr)
+ [pingr](https://CRAN.R-project.org/package=pingr)

## Installation

```
remotes::install_github("BigelowLab/cmr")
```

## Searching

The search process has 3 steps... (1) craft the URL, (2) make a request and capture the response and (3) extract the links to the various datasets.

#### Craft the URL

```{r}
suppressPackageStartupMessages({
  library(cmr)
  library(dplyr)
})

x <- search_collection(
    id = "C1996881146-POCLOUD",
    times = c("2021-01-01T10:00:00Z","2021-02-01T00:00:00Z"),
    form = 'url')

x
```

#### Making the request

With a suitable browser, you can make the request and see the results. But if your browser doesn't do pretty renderings of JSON data then is isn't worth it.   

```
# httr::BROWSE(x) - for browsing, pretty nice in Firefox
```

But without using a browser, we can extract the interesting bits - namely the links to the data.

```{r}
resp <- httr::GET(x)
resp
```

#### Unpack the request

Here we unpack the response. 
```{r}
links <- extract_collection(resp)
links
```

#### Combine the three steps into one

An example adapted from the [examples](https://cmr.earthdata.nasa.gov/search/site/docs/search/api.html#general-request-details)

Here I switch the example to MUR-GRHSST data set, so I use the MUR collection ID. MUR is posted once per day. We are interested in opendap, so we filter on `^.*OPeNDAP` in the `Description` variable.

```{r}
x <- search_collection(
    id = "C1996881146-POCLOUD",
    times = c("2021-01-01T10:00:00Z","2021-02-01T00:00:00Z"),
    description_pattern = "^.*OPeNDAP",
    verbose = TRUE) 
x
```


## Getting a token

In order to access the data, once you have found it, you need credentials.  CMR provides for a username-password combination to obtain a temporary token. For each session you can obtain a token, do you stuff, and then delete the token. Store you username and password in a text file called `.netrc` and save it in your home directory.  It should contain three items like this, but obviously with your own username and password. Read more about the configuration file [here](https://github.com/podaac/data-subscriber/blob/main/Subscriber.md).

```
machine urs.earthdata.nasa.gov
  username htubman
  password  xxxxxxxxxxxxxxxxxxxxxxx
```

Read the credentials, extra info will be added to your username and password.

```{r}
creds <- read_credentials()
creds
```

Now get a token.

```{r}
creds <- get_token(creds)
creds
```

After you have done you work, delete the token

```{r}
creds <- token_delete(creds)
creds
```


## Open the OPeNDAP resource

And it falls apart because `ncdf4::nc_open()` simply passes the url.  It's not really a 'thing' to pass credentials, too.

```{r}
library(ncdf4)
nc <- try(nc_open(x$URL[1]))
```
